### 2015-02-18 Docs/analysis/analysis.tex
update location of the Fortran postprocessing tools

\section{The {\tt AmrPostprocessing} Routines}
\label{sec:analysis}

The {\tt AmrPostprocessing/F\_Src/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

As a concrete example, running {\tt test2} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt AmrPostprocessing/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/AmrPostprocessing/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt test2} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

>>>>

\section{The {\tt Postprocessing} Routines}
\label{sec:analysis}

The {\tt BoxLib/Tools/Postprocessing/F\_Src/} directory contains a large
number of Fortran-based analysis routines for BoxLib datasets.  Many
of these can be used with both \maestro\ and the compressible
astrophysics code, \castro.

@@

As a concrete example, running {\tt reacting\_bubble} with particles enabled
will seed particles in the initial hotspot.  To plot the results,
first set your {\tt PYTHONPATH} environment variable to point to the
{\tt AmrPostprocessing/python/} directory, for example:
\begin{verbatim}
export PYTHONPATH="/home/username/development/AmrPostprocessing/python"
\end{verbatim}
This will allow python to see the {\tt parseparticles.py} routine.
For the {\tt reacting\_bubble} problem, the {\tt plotparticles.py} routine shows
how to plot the particle histories and make an animation of the
particles colored by the ash mass fraction.  This script is run as:
\begin{verbatim}
./plotparticles.py timestamp_*
\end{verbatim}

### 2015-02-18 Docs/managing_jobs/managingjobs.tex

Additionally, if the {\tt ftime} executable is in your path 
({\tt ftime.f90} lives in {\tt AmrPostprocessing/F\_src/}), then the
script will create a file called {\tt ftime.out} that lists the name of the
plotfile and the corresponding simulation time.

>>>>

Additionally, if the {\tt ftime} executable is in your path 
({\tt ftime.f90} lives in {\tt BoxLib/Tools/Postprocessing/F\_src/}), then the
script will create a file called {\tt ftime.out} that lists the name of the
plotfile and the corresponding simulation time.
